---
title: "Visualizing Fitness Surfaces"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# the problem

I was writing a review article with a couple colaborators, and we were trying to ilustrate how 
genetic covariation between traits could lead to macro evolutionary consequences. Our argument was
that this is really dependant on the shape of the adaptive surface, and how this interacts with 
within population variation. This is resonably complicated even in simple cases, so we wanted to have 
a descent figure to ilustrate the effect of covariation on long term selection. 

# plotting selection

my first attempt at this was using inkscape, but it felt really forced, and I don't have the 
illustrator skills to pull of a good looking figure if it's this complicated. I also felt like I was 
cheating if I didn't explicitly calculate the population trajectories in the fitness landscape. I didn't
think this would be a problem, but everyvody who looked at the drafts had something to say about the 
trajectories, so I decided to use R and calculate everything, since people's intuition varied so much.

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
